\chapter{Introduction} \label{chap:intro}

The purpose of this chapter is to introduce the motivation for the work, briefly describe the problem at hand and outline the work that will be developed, as well as the structure of the thesis.

\section{Motivation} \label{sec:motivation}

Collective software development requires the handling of merge conflicts, as conflicts between parallel work arise. Called merge conflicts, as they arise when this parallel work is merged, they vary in their difficulty of detection.
Common textual conflicts, where the same line is altered by multiple people, are automatically detected by version control systems, allowing amendments to be easily made. However not all conflicts are this easily detected and their introduction bring with it the addition of software bugs to the system.
The recent revolution in the field of Large Language Models (LLMs) may prove to add a valuable tool in tackling this situation.


\section{Problem} \label{sec:problem}




\section{Goal and Approach} \label{sec:approach}

In previously developed work, a Domain-Specific Language was designed which describes the changes made in a three-way merge.






\section{Thesis Structure} \label{sec:struct}

Para além da introdução, esta dissertação contém mais x capítulos.
No Capítulo~\ref{chap:sota}, é descrito o estado da arte e são
apresentados trabalhos relacionados. 
No Capítulo~\ref{chap:chap3}, ipsum dolor sit amet, consectetuer
adipiscing elit.
No Capítulo~\ref{chap:chap4} praesent sit amet sem. 
No Capítulo~\ref{chap:concl} posuere, ante non tristique
consectetuer, dui elit scelerisque augue, eu vehicula nibh nisi ac
est. 
